The effects of binarity on planet occurrence rates measured by transit surveys

### 2017-12-15 paper/simplest_effects.tex
paper: update figures and captions.

\begin{figure}[!tb]
    \begin{center}
        \includegraphics[width=.6\textwidth]{figures/errcases_rate_density_vs_radius_model_1_brokenx.pdf}
    \end{center}
    \vspace{-0.5cm}
    \caption{
        Inferred planet occurrence rates over $0.01r_\oplus$ bins in planet 
        radius,
        for Model \#1.
        This model has fixed stars, fixed planets, and twin binaries. 
        It assumes a twin binary fraction of ${\rm BF}=0.1$.
        If the true planet radius is $r_p$, all planets 
        detected in binaries will have apparent radii $r_a = r_p/\sqrt{2}$.
        We illustrate the individual biases by separating them.
        On this and future plots,
        ``only wrong $N_\star$'' means the only error is an incorrectly 
        assumed 
        number of selected stars;
        ``only wrong $Q$'' means the only error is an incorrectly assumed 
        completeness (including both miscalculated $p_{\rm tra}$ 
        and fraction of selected stars that are searchable, $p_{\rm det}$);
        ``only wrong $r_a$'' means the only error is in miscalculated        
        planetary radii, due to both transit depth dilution and also wrongly 
        assumed host star radii.
    }
    \label{fig:errcases_model_1}
\end{figure}

>>>>

\begin{figure}[!tb]
    \begin{center}
        \includegraphics[width=.6\textwidth]{figures/occ_rate_vs_radius_model_1_brokenx.pdf}
    \end{center}
    \vspace{-0.5cm}
    \caption{
        Inferred occurrence rates over $0.01r_\oplus$ bins in planet 
        radius,for Model \#1.
        This model has fixed stars, fixed planets, and twin binaries. 
        Further, a twin binary fraction of ${\rm BF}=0.1$ is assumed, and all 
        planets are {\bf TODO}.
        If the true planet radius is $r_p$, all planets detected in binaries 
        will have apparent radii $r_a = r_p/\sqrt{2}$.
    }
    \label{fig:errcases_model_1}
\end{figure}
